Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-11 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
Section VI

\begin{figure}[t]
\includegraphics[width=0.9\columnwidth]{figs/tmp_GW150914_intrinsic_params_remnant.pdf}
\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
detector-frame remnant mass $(1 + z) \, M_f$ for GW150915, using the same waveform model,
but without (blue contours) and with the non-GR parameters different from zero (orange contours, for
dCS gravity and $j=0$). The contours represent 90\% credible regions.
%
We see that the introduction of the non-GR parameters does not bias the
inference on the source parameters.
}
\label{fig:corner_plot}
\end{figure}

@@

@@

\section{Details of the determination of the theory-specific
ParSpec coefficients}
\label{app:map_details}

>>>>

\begin{figure}[t]
\includegraphics[width=0.9\columnwidth]{figs/tmp_GW150914_intrinsic_params_remnant.pdf}
\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
detector-frame remnant mass $(1 + z) \, M_f$ for GW150914, using the same waveform model,
but without (blue contours) \agcomm{colors are not up to date; needs to be 
finalised after we finalise the color scheme} and with the non-GR parameters 
different from zero (orange contours, for
dCS gravity and $N_{\rm max}=0$). The contours represent 90\% credible \sout{regions}\ag{levels}\agcomm{we have to be particular about the use of credible regions. If its 2D they are ``levels", if they are 1D then ``intervals". If we are quoting the difference of the 1D intervals, then we say ``credible bounds"}.
%
We see that the introduction of the non-GR parameters does not bias the
inference on the source parameters.
}
\label{fig:corner_plot}
\end{figure}

@@

\agcomm{Mention that we do not use the high-spin version of the fits, and refer to the 
chif measurements Fig.~\ref{fig:corner_plot} (which should be near the text here).}

\agcomm{Mention that our alternate ringdown formalism does not bias estimates of GR quantities 
and refer to Fig.~\ref{fig:corner_plot_all}}

\begin{figure*}[t]
\includegraphics[width=0.9\textwidth]{figs/tmp_GW150914_intrinsic_params.pdf}
\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
detector-frame remnant mass $(1 + z) \, M_f$ for GW150914, using the same waveform model,
but without (blue contours)\agcomm{colors to be updated.} and with the non-GR parameters different from zero (orange contours, for
dCS gravity and $N_{\rm max}=0$). The contours represent 90\% credible levels.
%
We see that the introduction of the non-GR parameters does not bias the
inference on the source parameters.
}
\label{fig:corner_plot_all}
\end{figure*}

@@

\section{Details of the determination of the theory-specific
ParSpec coefficients}
\label{app:map_details}
\agcomm{Reorder sections, such that the appendix comes after the Acknowledgments?}

\agcomm{Have not gone through the appendices, because there might be sections that still
need to be completed.}
